### 2019-01-04 revisions/review-responses.tex

		        Additionally, the presence of rubidium, strontium, cesium, and barium in
		         the core are disadvantageous to reactor physics. In fact, SaltProc fully 
		         removes all these elements every 3435 days (not a small mass fraction 
		         every 3 days) which causes the multiplication factor to jump by 
		        approximately 450 pcm, and limits using the batch approach for online 
		        reprocessing simulations. In future versions of SaltProc this drawback 
		        will be eliminated by removing elements with longer cycle times (seminoble 
		        metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
		        Only mass fraction (calculated separately for each reprocessing group) 
		        will be removed every depletion step (e.g. 3 days) instead of removing 
		        100\% of element atoms after cycle time. 
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                Thank you for the recommendation. Atom density was chosen for publication-to-						publication comparison (e.g. Park \emph{et al.} and Betzler \emph{et al.}
                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
                be more understandable for the reader and will be added in a future releases.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, Fig 9: What are the wiggles and dips , especially 
        seen for Np235?
        \begin{solution}
		        Explanation of this phenomena has been added as follows:

		         Small dips in neptunium and plutonium number density every 16 years are 
		         caused by removing $^{237}$Np, $^{242}$Pu (included in Processing group 
		         ``Higher nuclides'', see Table~\ref{tab:reprocessing_list}) which decays
        		  into $^{235}$Np, $^{239}$Pu, respectively. 
        \end{solution}

### 2019-01-04 methods.tex

Current version of SaltProc only allows separate out 100\% of specific elements 
or group of elements (e.g. Processing Groups as described in 
Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
This approach works well for fast-removing elements (gases, noble metals, 
protactinium) which should be removed each depletion step. Unfortunately, 
for the elements with longer cycle time (i.e. rare earths should be removed 
every 50 days) this simplified approach leads to oscillatory behavior of all
major parameters. In future releases of SaltProc this drawback will be eliminated 
by removing elements with longer cycle times using different method: only mass 
fraction (calculated separately for each reprocessing group) will be removed each
 depletion step (e.g. 3 days).

>>>>

Current version of SaltProc only allows separate out 100\% of specific elements 
or group of elements (e.g. Processing Groups as described in 
Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. That is 
simplification because in reality fuel salt resides approximately 1/2 of total time 
in the core and rest of the time in the primary loop pipes and the heat exchanger.  
This approach works well for fast-removing elements (gases, noble metals, 
protactinium) which should be removed each depletion step. Unfortunately, 
for the elements with longer cycle time (i.e. rare earths should be removed 
every 50 days) this simplified approach leads to oscillatory behavior of all
major parameters. In future releases of SaltProc this drawback will be eliminated 
by removing elements with longer cycle times using different method: only mass 
fraction (calculated separately for each reprocessing group) will be removed each
 depletion step or batch (e.g. in the current work it was chosen 3 days).
